Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-06 ms/manuscript.Rmd
Fix taxon with widest lat text

```{r limits-stats}
# Find the species with the widest latitudinal distribution
taxon_with_widest_lat <- lat_span_summary %>%
  mutate(lat_span = max_lat - min_lat) %>%
  slice_max(lat_span, with_ties = FALSE) %>%
  left_join(green_list, by = "taxon") %>%
  # Parse out species name and author
  mutate(gn_parse_tidy(.$scientific_name) %>% select(canonicalsimple, authorship)) %>%
  mutate(text = glue("*{canonicalsimple}* {authorship}"))

>>>>

```{r limits-stats}
# Find the species with the widest latitudinal distribution
taxon_with_widest_lat <- lat_span_summary %>%
  mutate(lat_span = max_lat - min_lat) %>%
  slice_max(lat_span) %>%
  # Add formatted scientific name
  left_join(
    tibble(
      taxon = "Pteridium_aquilinum_japonicum",
      text = "*Pteridium aquilinum* (L.) Kuhn subsp. *japonicum* (Nakai) A. et S.Löve"
    ),
    by = "taxon"
  ) %>%
  # Round off latitude
  mutate(across(c(min_lat, max_lat), ~round(., 2)))

# Make sure the taxon_with_widest_lat is what we expect
assert_that(
  taxon_with_widest_lat$taxon == "Pteridium_aquilinum_japonicum",
  msg = "Taxon with widest latitude wasn't Pteridium_aquilinum_japonicum")
